%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Bachelor Degree in Computer Science and Engineering} % Degree
    {University of Vigo} % Institution
    {Vigo, Spain} % Location
    {Sep. 2011 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
	\item {Principal subjects covered: Software Engineering, Software design and patterns, Networking and Systems Administration.}
	\item {Score: B}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master Degree in Free Software} % Degree
    {Rey Juan Carlos University \& Igalia} % Institution
    {A Coruña \& Madrid, Spain} % Location
    {Sep. 2011 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
	\item {Principal subjects covered: Free software communities, Free software licensing, Unix/Linux Systems Administration.}
	\item {Principal subjects covered: Desktop and mobile development(Meego \& Android), Web development(Java \& ZK Framework).}
	\item {Score: B}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bachelor in Computer Science} % Degree
    {University of Vigo} % Institution
    {Vigo, Spain} % Location
    {Sep. 2005 - Jul. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
	\item {Principal subjects covered: Software Engineering, Software design and patterns, C/C++, Java, C\#, Python, PHP.}
	\item {Score: B}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Higher level vocational training at computer Systems management} % Degree
    {IES Teis} % Institution
    {Vigo, Spain} % Location
    {Sep. 2003 - Jun. 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
	\item {Principal subjects covered: Windows/Linux Systems Administration, Database Administration, Networking.}
	\item {Score: B}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
