%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Staff Systems Engineer} % Job title
    {ServiceNow} % Organization
    {Dublin, Ireland} % Location
    {Oct. 2018 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Infrastructure Systems Engineer for ServiceNow Private Cloud }
        \item { Architect Platform as a Service (PaaS) based on Red Hat OpenShift }
        \item { PowerDNS, OpenLDAP, Automation with Ansible and Ansible Tower, Puppet, VMWAre }
        \item {Azure Service Architecture Design Plan and Implementation }
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Cloud Consultant} % Job title
    {Red Hat} % Organization
    {Madrid, Spain} % Location
    {May. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Cloud Consultant mainly focused on OpenShift, K8s and automation.}
        \item {Main activities \& responsabilities: Advice customers with large OpenShift installations on different aspects, from security recommendations, to fine tuning for better performance, scalability and high availability.}
        \item {Developed YaaB: (Yet another Ansible Benchmarking tool) Ansible playbooks to launch a number of different benchmarking tools to measure performance on RHEL-based systems.}
        \item {Developed Goldem: A tool to automate golden image creation, with the same goal as packer.io. }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Daft.ie} % Organization
    {Dublin, Ireland} % Location
    {Jul. 2016 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {DevOps Engineering for Daft.ie.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Linux Professional Institute Instructor} % Job title
    {PCarrier} % Organization
    {A Coruña, Spain} % Location
    {Nov. 2011 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instructor for LPIC Certifications levels 1,2,3.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Security Researcher} % Job title
    {GRADIANT} % Organization
    {Vigo, Spain} % Location
    {Jan. 2014 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Evaluating security mechanisms for different projects and environments focused on authentication and cryptography.}
        \item {Implemented an ad-hoc OAuth PHP server for authentication.}
        \item {Lead engineer on Calipesca project.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Systems Engineer} % Job title
    {Electronic Arts (Vendor)} % Organization
    {A Coruña, Spain \& Austin, U.S.A} % Location
    {Oct. 2011 - Jan. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team Leader for the L3 Unix Online gaming platform at Electronic Arts (Fleet of +15k Red Hat Servers).}
        \item {Main activities \& responsabilities: DNS administration, LDAP administration, SSL certification creation/renewal, Troubleshooting, VMWare/Xen/KVM virtualization, MySQL \& Oracle administration, AWS, PCI environment administration. }
	\item {Full server cycle management: Deployment(Cobbler, Spacewalk, Puppet), Management/Troubleshoot, Decommission.} 
	\item {Security projects: DNS blackhole, real-time rootkit \& malware detection.} 
	\item {Implemented ad-hoc scripts for various purposes.} 
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {WirelessGalicia} % Organization
    {Vigo, Spain} % Location
    {Sep. 2010 - Jun. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Wireless Sensor Network (WSN) backend in Python.}
        \item {Implemented PHP sites with Symfony2 framework.}
      \end{cvitems} 
    }
%---------------------------------------------------------
  \cventry
    {Systems Engineer Trainee} % Job title
    {Quality Management} % Organization
    {Vigo, Spain} % Location
    {Apr. 2005 - Nov. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed systems administration tasks: Firewalling, Mail server, Backups, VPN, VoIP, Troubleshooting.}
      \end{cvitems}
    }

\end{cventries}
