%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
% \geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\name{}{Jorge Rúa Riveiro}
\position{Systems Engineer{\enskip\cdotp\enskip}Security Expert}
\address{Avda. Camelias 82 6A. Vigo, Spain}

\mobile{(+34) 617 624 715} 
\email{jruariveiro@gmail.com}
% \homepage{www.abilityjob.com}
\github{jruariveiro}
\linkedin{jorgeruariveiro}
\twitter{@jruariveiro}
\skype{jruariveiro}
% \extrainfo{extra informations}

\quote{``Cogito, ergo sum."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Etsy Recruitment Team}
  {66, 67 Strand Street Great, Dublin}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Senior Web Operations Engineer}
% How the letter is opened
\letteropening{Dear Ms. Cooney,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Jorge Rúa Riveiro.~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}

You may think I have choosen this cover letter \& CV color scheme by random, but that's not the case. I have choosen orange for two reasons, one and most important is Etsy logo, and the other is because orange is one of the colors of Ireland's flag. Orange is also a color full of vitality, enthusiasm and fun!

This is one of my main personal qualities, I love to pay attention to details. Details make the difference between good and great. Another of my qualities is playing and working as a team, as there are no losers on a winning team, and no winners on a losing team.

Furthermore I have the confidence and perseverance to get things done, because is not about how many things you start, is about how many you finish, always enjoying along the way!

\lettersection{Why Etsy?}

Etsy is the type of company which gives me the opportunity to participate in a challenging environment, where I can learn from others and collaborate in an innovative manner.

I love the culture of transparency at Etsy, where people is the most valuable asset for the company.

Etsy is a great place to work, plenty of talented people from different cultures around the world.  

\lettersection{Why Me?}

The position of Senior Web Operations Engineer aligns with my skills and experience. I am enthusiastic about expanding my knowledge in systems performance, network protocols, security among other non-technical interesting topics!

I am also the kind of critical and analytical person that is always looking for improving previously established methods, providing new solutions and ideas.
    
\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
